
\section{Experience}

\outerlist{

\entrybig
	{\textbf{On Running}}{Berlin, Germany}
	{Senior Software Engineer}{April 2020\textendash Present}
    {Developing integrations between Salesforce, Microsoft Dynamics 365 and Digital Storefront for the new ERP infrastructure to support the company's explosive growth.}
\innerlist{
    \entry{Designing and implementing a serverless architecture.}
    \entry{Acquiring continuous knowledge and mentor the team.}
    \entry{Collaborating in automating the deployment strategy with modern CI/CD tools.}
    \entry{Influenced in recruiting for new team members.}
    \entry{Organize and host weekly fitness classes.}
	\entry{\textbf{Technologies}: AWS, Azure, Azure Function Apps, Azure SQL DB, Typescript, Terraform.}
	\entry{\textbf{Methodology}: Agile, Scrum.}
}

\entrybig
	{\textbf{Digital:Lab by Volkswagen}}{Berlin, Germany}
	{Full Stack Software Engineer}{September 2018\textendash March 2020}
	{Championed ownership and development of new products in an entrepreneurial methodology.}
\innerlist{
    \entry{Designed and implemented modern microservice based architecture.}
    \entry{Created and maintained automated deployment strategy with state-of-the-art CI/CD technologies.}
    \entry{Co-Innovated end-to-end features with the UI/UX team.}
    \entry{Spearheaded implementation of quarterly OKRs.}
    \entry{Organized and hosted weekly fitness classes.}
	\entry{\textbf{Technologies}: React, Angular, TypeScript, Kotlin, Spring Boot, Cloud Foundry, Concourse CI.}
	\entry{\textbf{Methodology}: Extreme Programming, TDD, Pair Programming.}
}

\entrybig
	{\textbf{SAP Innovation Center}}{Potsdam, Germany}
	{Full Stack Software Engineer}{July 2016\textendash August 2018}
	{Develop a native cloud solution addressing the needs of corporates in managing their real estate assets and their workspace.}
\innerlist{
    \entry{Designed and implemented new features end-to-end.}
    \entry{Introduce End-to-End testing.}
    \entry{Involved in recruiting new team members.}
    \entry{Trained junior team members to be productive members of the team.}
	\entry{\textbf{Technologies}: Angular 4, TypeScript, CSS, Java, Spring, SAP Hana Cloud Platform}
	\entry{\textbf{Methodology}: Agile, Scrum.}
}

\entrybig
	{\textbf{Fraunhofer Institute for Applied Information Technology FIT}}{Sankt Augustin, Germany}
	{Master Thesis Student}{June 2015\textendash December 2015}
    {Thesis: Layout-Aware Semantic Information Extraction from Semi-structured Documents.}
\innerlist{
    \entry{Design and implement a rule-based approach to extract semantic information from PDF/Word documents.}
}

\entrybig
	{\textbf{Helius Systems}}{Tirana, Albania}
	{Full Stack Software Engineer}{September 2010\textendash August 2013}
	{Developed and maintained solutions used by clients of varying sizes.}
\innerlist{
    \entry{Implement end-to-end new features, from database design to UI implementation.}
    \entry{Implement integration with different external partners.}
    \entry{Influenced in recruiting for new team members.}
    \entry{Prepare management reporting module: including daily C-level overview.}
	\entry{\textbf{Technologies}: Visual Basic .NET, C\# and Microsoft SQL Server 2012.}
}
}